HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
edits

\subsection{Verbal Structures Only?}

@@

\subsection{Cost of Structural Annotation}

@@

\subsection{One vs. Two Structures}

@@

\subsection{Importance of Alignment}

In HMEANT, the alignment between the (source and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that modifications to the two structures are desirable and appropriate
at the alignment stage, to avoid unduly penalization due to spurious diverges in
the structures.\oa{I didn't understand this}
The same issue was observed by HMEANT authors themselves \parcite{XXXcite}
\XXX{cite this: http://repository.ust.hk/ir/Record/1783.1-66107}: the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

@@

\subsection{Monolingual vs. Bilingual Evaluation}
HUME diverges from HMEANT (and also from the shallow automatic measures
like BLEU or METEOR) in not requiring a reference.
Instead, it compares the source directly with the output translation.

@@

\subsection{Technical Differences}

@@

\subsection{XXX to be removed}

In the *MEANT papers they mainly test by either
A) correlating the metric to ranking judgements; or
B) using automated versions of the metric for tuning MT systems

I think neither is particularly convincing, but I'm not sure at the moment what we replace them with. Dekai also made a claim about the *MEANT metrics being "interpretable" in the sense that they could guide you towards semantic errors that the MT system may be making, however I don't recall seeing this done in his papers.

By the claim that HMEANT explains things, Dekai probably means that the score is decomposable, but so is UCCA-Eval and even BLEU. And UCCA-Eval has one benefit over HMEANT: it points to words in the MT output that are aligned with something but do not convey the meaning well (and we know which part of the source meaning). Pure HMEANT might say only that some part of the MT output has no clear frames whatsover (and we do not know which part of the source/reference, unless we add the word alignments).

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as being able to determine
whether the translation accurately conveys the same information as the source is here paramount.

%particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
%information for speakers of languages other than English, and in this domain accurate transfer of meaning is
%paramount.

The experiment seeks to address two questions:

\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how much in each.}.

>>>>

\paragraph{Verbal Structures Only?}

@@

\paragraph{Cost of Structural Annotation}

@@

\paragraph{One vs. Two Structures}

@@

\paragraph{Importance of Alignment}

In HMEANT, the alignment between the (reference and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that sometimes, the structures of the reference and candidate
translations diverge without any good reason, for instance due to a different
interpretation of a PP-attachment, the verb can have one additional modifier in
one of the structures. It would be desirable to allow updates to the structural
annotations also at the alignment stage
to avoid unduly penalization due to such a spurious diverge.
The same issue was observed by HMEANT authors themselves
\parcite{lo:wu:reliability:2014}:
the 
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

@@

\paragraph{Monolingual vs. Bilingual Evaluation}
HUME diverges from HMEANT (and also from the shallow automatic measures
like BLEU or METEOR) in not requiring a reference.
Instead, it compares the source directly with the output translation.

@@

\paragraph{Technical Differences}

@@

% \subsection{ to be removed}
% 
% In the *MEANT papers they mainly test by either
% A) correlating the metric to ranking judgements; or
% B) using automated versions of the metric for tuning MT systems
% 
% I think neither is particularly convincing, but I'm not sure at the moment what we replace them with. Dekai also made a claim about the *MEANT metrics being "interpretable" in the sense that they could guide you towards semantic errors that the MT system may be making, however I don't recall seeing this done in his papers. 
% 
% By the claim that HMEANT explains things, Dekai probably means that the score is decomposable, but so is UCCA-Eval and even BLEU. And UCCA-Eval has one benefit over HMEANT: it points to words in the MT output that are aligned with something but do not convey the meaning well (and we know which part of the source meaning). Pure HMEANT might say only that some part of the MT output has no clear frames whatsover (and we do not know which part of the source/reference, unless we add the word alignments).
% 
%

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain. We are 
particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
information for speakers of languages other than English, and in this domain accurate transfer of meaning is
paramount.

Our annotation experiment sought to address the following questions:
\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.
